Trade Reviews

### 2019-04-06 tradeReview.Rmd
Missed one data set for accent mark cleanup

draft_results <- draft_results_raw %>% 
  select(pick, player)
```

@@

trade_df %>% saveRDS("data/tradeReview_20190405.Rds")
```

>>>>

draft_results <- draft_results_raw %>% 
  mutate(player = chartr("áéóíñú", "aeoinu", player)) %>% 
  select(pick, player)
```

@@

trade_df %>% saveRDS("data/tradeReview_20190405.Rds")

trade_df %>% 
  mutate(z_sum = round(z_sum)) %>% 
  arrange(z_sum %>% desc, pick) %>% 
  View()
```
